Comparative Evaluation of Spark and Flink Stream Processing

### 2017-03-02 paper/paper.tex
Updated read me.

\par In recent years, Big Data is considered as one of the most appealing topics in Information Technology, it has gained increasing attention of professionals in industry and academics, as a result of the fact that the amount of data we generate is increasing exponentially \cite{idc} that generated from social media platforms, mobile phones, IoT and finical transactions, etc. Moreover, recent years showed a rapid development of Big Data frameworks such as Apache Spark and Apache Flink that provide more and efficient data processing capabilities.
 \par The Big Data is a method to process not just only large datasets (volume), but also the data that arrives in high rate (velocity), and it comes in all kinds of data format (variety) (i.e., 3Vs of Big Data (Volume, Velocity, Variety)) \cite{svs}.

@@

\subsubsection{Statistics Computation per Trajectory}
In first stream processing workload, we construct stream of trajectories by considering  the aircraft's positions (i.e., ADS-B messages) that belong to the same aircraft as trajectory. Moreover, we continuously compute and aggregate statistics for each arriving position in a  trajectory . As example of computed statistics indexes speed mean, mean of location coordinates, min and max altitude, etc. In this workload, we  cover the parallel receiving of input data stream, state-full aggregation on input data stream, and preserving the right order of the stream's records.
The implementation details of this workload in Spark and Flink are presented in the following: 
\begin{itemize}
\item {\bf{Implementation in Spark }}

>>>>

\par In recent years, Big Data is considered as one of the most appealing topics in Information Technology, it has gained increasing attention of professionals in industry and academia, as a result of the fact that the amount of data we generate is increasing exponentially \cite{idc} that generated from social media platforms, mobile phones, IoT and finical transactions, etc. Moreover, recent years showed a rapid development of Big Data frameworks such as Apache Spark and Apache Flink that provide more and efficient data processing capabilities.
 \par The Big Data is a method to process not just only large datasets (volume), but also the data that arrives in high rate (velocity), and it comes in all kinds of data format (variety) (i.e., 3Vs of Big Data (Volume, Velocity, Variety)) \cite{svs}.

@@

\subsubsection{Statistics Computation per Trajectory}
In the first stream processing workload, we construct stream of trajectories by considering  the aircraft's positions (i.e., ADS-B messages) that belong to the same aircraft as trajectory. Moreover, we continuously compute and aggregate statistics for each arriving position in a trajectory . As example of computed statistics quantities speed mean, mean of location coordinates, min and max altitude, etc. In this workload, we  cover the parallel receiving of input data stream, statefull aggregation over the input data stream, and preserving the correct order of the stream's records.
The implementation details of this workload in Spark and Flink are presented in the following: 
\begin{itemize}
\item {\bf{Implementation in Spark }}
